\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-19 WOOT/Files/experiment.tex
[experiment] user study

Overview, \tool in experiments consist of a USB Type-C hub with HDMI and USB port,
a Raspberry Pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.
The powerbank is used to supply a piece of Raspberry Pi 4B and charge victim's device.
The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports.

\outline{Attack Modes}

@@

@@

@@

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary powerbanks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user unconsciously connect his/her device to \tool. 
He/She can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment.
\yechang{tired, go to bed}

\subsection{evaluation}

>>>>

Overview, \tool in experiments consist of a USB Type-C hub with HDMI and USB port,
a Raspberry Pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.
The powerbank is used to supply a piece of Raspberry Pi 4B and charge victim's device.
The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports. The USB Type-C hub is used to connect HID devices and transmit video stream from victim's device to HDMI port. The video stream then will be capture by the Raspberry Pi 4B through the video capture card.

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
	\caption{Two power banks station products}
	\label{fig:PBS_products}
\end{figure}

@@

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
	\caption{Bar/QR code payment procedure}
	\label{fig:qr_payment_procedure}
\end{figure}

@@

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary power banks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user unconsciously connect his/her device to \tool. 
He/She can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.

\subsection{User study}

In order to check what can be obtained by \tool, we conduct a user study in order to check the performance of \tool in Privacy extraction mode.

\subsubsection{Setup}

\subsubsection{Scenario}

We invited 6 volunteers to our lab room. Volunteers take turns to operate their phones for half an hour while \tool is connected. Before the study, we did not reveal the function of \tool and asked the volunteers to connect their phones to \tool as a normal power bank (ignoring its larger size). 
After the study, we told them our attack, checked recorded videos together, and confirmed the consent to study the information in recorded videos, Subject to efficiency reasons, we ask them to use phones like when they use the shared power bank outside.

\subsubsection{Result}

After collecting the videos, we used both automatic and manual methods to analyze the video. In the automatic analysis, we use a script to simply perform OCR recognition to each frame in the recorded video and store all OCR results into a database in a format of ``frame number - text by OCR''. At last, there are 38329 pieces of data collected among 6 volunteers. In the manual analysis, we replay the recorded video and extract sensitive information manually.

In terms of automatic analysis, OCR results of all frames are already stored in the database and can be used at hand. With these results, we can learn what issues the victim is browsing. Additionally, some keywords often appear with users' input data because they are often used as labels of input boxes, such as ``account'', ``username''. Such keywords are more likely to lead us to discover user-specific data. For example, in Figure~\ref{fig:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig. The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

\begin{figure}[hbtp]
	\centering
	\includegraphics[width=\linewidth]{./Figs/ocr_keyword_example.png}
	\caption{Search ``account'' in all OCR results}
	\label{fig:ocr_keyword_example}
\end{figure}

In terms of manual analysis, data collected are listed in table ~\ref{table:information_extracted}. Accounts of internet applications such as Apple ID, iCloud, Facebook, Twitter, WeChat, QQ, Alipay can be obtained. Additionally, all typing inputs are on the virtual keyboard (including the system keyboard and the built-in security keyboard of the financial app), which can be clearly recorded. Noticed that, we can obtain the plain text of password typed such as the WiFi password and the Alipay password. Furthermore, the received SMS verification code (usually is used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

In summary, we can no longer directly peek at the user’s password on the lock screen. But if the user unconsciously unlocks the screen, we can still check all information presented on the screen, extract private information including but not limited to social accounts, bank accounts, personal financial situation, etc. It is worth noting that the so-called secure keyboards built into some financial apps just simply disrupt the keyboard sequence and cannot prevent attacks similar to \tool.
